### 2021-05-16 manuscripts/owp_fim3_2020/sections/abstract_plainTextSummary.tex
slight changes

\section*{Plain Language Summary}
Flooding is one of the most impactful natural disasters on life and property.
So having high quality flood forecasts enables people to protect lives and property.
The United States National Water Model seeks to provide flood forecasts for the entire country so that adequate warnings can be raised to the public to enable safe evacuations and protective measures.
The National Water Model produces flow rates at river segments so additional work is needed to convert these flow rates to inundation extents so that flood maps can be developed.
The Office of Water Prediction Flood Inundation Mapping Version 3 provides enhancements to existing capabilities to provide these flood maps as a service.
The maps were compared to other, more rigorous models and shown to perform well when compared to previous versions.
%

>>>>

\section*{Plain Language Summary}
Flooding is one of the most impactful natural disasters on life and property.
The United States National Water Model (NWM) seeks to provide flood forecasts for the entire country so that adequate warnings can be raised to the public to enable safe evacuations and protective measures.
In order to convert forecasts flow rates from the NWM to inundation extents, a model is used that converts elevations relative to sea-level to elevations relative to the nearest river bottom elevation.
This model known as Height Above Nearest Drainage (HAND) suffers fro
The maps were compared to other, more rigorous models and shown to perform well when compared to previous versions.
%
